---
title: "IV"
author: "Kei Sakamoto"
output: word_document
---

# IV esttimatorのRでの計算方法は4種類
###①両辺IVとのcovarianceとる
###②手動で1st stage とsecond stage を実行
###③コマンドのivreg
###④コマンドのtsls



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
load("~/計量経済学演習/R data sets for 5e/mroz.RData")
mroz<-data
library(AER);library(stargazer)
```

### Extract non-missing sample
```{r}
sampleset <- subset(mroz, !is.na(wage))
```

#### OLS slope parameter manually
```{r}
with(sampleset, cov(log(wage),educ) / var(educ) )
```

### ①IV slope parameter manually
```{r}
with(sampleset, cov(log(wage),fatheduc) / cov(educ,fatheduc) )
```

#### OLS automatically
```{r}
reg.ols <-   lm(log(wage) ~ educ, data=sampleset)
```

### ③IV automatically 
```{r}
reg.iv <- ivreg(log(wage) ~ educ | fatheduc, data=sampleset) 
```

```{r}
stargazer(reg.ols,reg.iv, type="text")
```
#### identical estimates as manual iv (①)



# Add exper and I(exper^2) to the model as  exogenous regressors and motheduc as IV

### ②
```{r}
### 1st stage: reduced form

stage1 <- lm(educ~exper+I(exper^2)+motheduc+fatheduc, data=sampleset)

### 2nd stage
(man.2SLS<-lm(log(wage)~fitted(stage1)+exper+I(exper^2), data=sampleset))
```


### ④Automatic 2SLS estimation
```{r}
library(sem)
(aut.2SLS<-tsls(log(wage)~educ+exper+I(exper^2),instruments=~motheduc+fatheduc+exper+I(exper^2),data=sampleset))

```

#### identical estimates as ②


# Test of endogeneity(exogeneity) for (endogenous)regressor (not for IV but )
```{r}
stage2<-lm(log(wage)~educ+exper+I(exper^2)+resid(stage1),data=sampleset)

```

### results including t tests
```{r}
coeftest(stage2)
```
#### null hypothesis that coef of resid(stage1) is marginally rejected at significatce level 10% , this indicates endogeneity of educ .


# Test overidentifying restrictions (test of exogeneity for composit IV)

### auxiliary reg(composit IV が 2nd stageのerror と相関持ってたらまずい。)
```{r}
res.aux<-lm(resid(aut.2SLS)~exper+I(exper^2)+motheduc+fatheduc, data=sampleset) 
```

### Calculations for test
```{r}
( r2 <- summary(res.aux)$r.squared )
( n <- nobs(res.aux) )
( teststat <- n*r2 )
( pval <- 1-pchisq(teststat,1) )
```

### we cannot reject exogeneity of composit IV because of  p-value :0.53 