---
title: "[Example8-2] Heteroskedasticity-Robust SE"
author: "Kei Sakamoto"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
load("~/計量経済学演習/R data sets for 5e/gpa3.RData")
gpa3<-data
```

```{r}
library(lmtest); library(car) #lmtest for coeftest,car for linearHypothesis
```

### Estimate model (*only for spring data*)
```{r}
reg <- lm(cumgpa~sat+hsperc+tothrs+female+black+white, 
                                     data=gpa3, subset=(spring==1))
```

### t-test with usual SE (impose the assumption of homoskedasticity)
```{r}
coeftest(reg)
```

### with Refined White heteroscedasticity-robust SE
```{r}
coeftest(reg, vcov=hccm)
```
#### satなどvariable in interestのcoefのseは大きくなっているのでt-stat小さくなりp-valueは大きくなるので若干rejectしづらくなるがいずれにしろ1% significantであることは変わらない。

## F-Tests using different variance-covariance formulas
```{r}
myH0 <- c("black","white")
```
### ①Ususal VCOV(u is homoskedastic in black and white)
```{r}
linearHypothesis(reg, myH0)
```

### ②Refined White VCOV
```{r}
linearHypothesis(reg, myH0, vcov=hccm)
```

### ③Classical White VCOV
```{r}
linearHypothesis(reg, myH0, vcov=hccm(reg,type="hc0"))
```

#### どれも対して結果変わらんのでheteroskedastidityに対するsensitivityは高くはないって感じ